Determining the direction of causality in the face of measurement error

### 2016-02-16 docs/manuscript.Rmd
word doc works well

---
title: "Determining the direction of causality in the face of measurement error"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  word_document
bibliography: manuscript.bib
csl: nature.csl
---

>>>>

---
title: "Determining the direction of causality in the face of measurement error"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  pdf_document:
    keep_tex: true
bibliography: manuscript.bib
csl: nature.csl
---
